---
title:  | 
  | Ni Coarsening in Li~4~Ti~5~O~12~ Anode Composites
author: "William Huddleston"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: false
    number_sections: false
    toc_depth: 6
    highlight: tango
  html_document:
    toc: yes
urlcolor: blue
---

```{r setup, include=FALSE}
#SETUP OF LIBRARIES
knitr::opts_chunk$set(echo = FALSE) #set echo to FALSE to hide code
#knitr::opts_chunk$set(fig.pos = 'H')
library(tidyverse)
library(ggplot2)
library(GGally)
#library(gdata)
library(leaps)
library(MASS)
library(wesanderson)
library(mclust)
library(scales)
library(ggridges)
library(plotly)

#Alternative titles:
#Processing and Percolation of Li~4~Ti~5~O~12~-Ni Composite Anodes
#Densification and Coarsening of Li~4~Ti~5~O~12~-Ni Composite Anodes
```

# Introduction

$R^{3} - R_{o}^{3} = \frac{8 \gamma C_{\infty}V_{M}^{2}D}{9R_{g}T} t$

$D = D_o*e^{-(Ea/ kT)}$

$\sigma_{eff} = K_{1}\sigma_{o}(n-n_{c})^\mu$

$K_{1}= \frac{\gamma}{(1-n_{c})^\mu}$ 

$n_{c}^{P} = \frac{n_{c}^{100}}{(1-P)}$

# Experimental Methods

![LTO dilatometry and densification rate. Sintering temperatures are denoted with vertical dashed lines.](./SemProj-Images/LTODil){width=75%}


![Raw and processed SEM image for a 20vol.% Ni sample sintered at 900C for 5hrs. Scale bar is 5$\mu$m.](./SemProj-Images/imageprocessing){width=75%}

# Results and Discussion

## Percolation

![Electrical conductivity as a function of nickel volume content.](./SemProj-Images/PercolationResults)

$\sigma_{eff} = K_{1}\sigma_{o}(n-n_{c})^\mu$

## Coarsening

By rearranging the Ostwald ripening model:

$\frac{(R^{3} - R_{o}^{3})T}t = \frac{8 \gamma C_{\infty}V_{M}^{2}D}{9R_{g}}$

and introducing the exponential temperature dependence:

$\frac{(R^{3} - R_{o}^{3})T}t = \frac{8 \gamma C_{\infty}V_{M}^{2}D_oe^{-(Ea/ kT)}}{9R_{g}}$

A simplified form may be achieved through combination of constants.

$W_o = \frac{8 \gamma C_{\infty}V_{M}^{2}D_o}{9R_{g}}$

$\frac{(R^{3} - R_{o}^{3})T}t = W_oe^{-(Ea/ kT)}$

A Linear model was reached in the form $y = b + mx$ by taking the natural log :

$ln[\frac{(R^{3} - R_{o}^{3})T}t] = ln[W_oe^{-(Ea/ kT)}]$

$ln[\frac{(R^{3} - R_{o}^{3})T}t] = ln[W_o] + \frac{-Ea}{k} \frac{1}T$

$ln[\frac{(R^{3} - R_{o}^{3})T}t] = ln[W_o] + \frac{-Ea}{k} \frac{1}T + \beta (V_{Ni})$

![A) Composition (Ni vol%) Variable (Left to Right Increasing) B) Temperature Variable (Left to Right Increasing)](./SemProj-Images/psdmatrix)

```{r, fig.cap="Representative particle area distribution. The mean area is denoted by a red vertical line and the data shown is for 900C-5hrs-10Ni."}

#Histogram plotting

sampleID <- "WH09"

mean1 <- df_particles %>%
  dplyr::select(2,3,8:10,15,17,18) %>%
  filter(substr(Label,0,4) == sampleID) %>%
  filter(Area >= 0.005) %>%
  summarise(mean = mean(Area))

median1 <- df_particles %>%
  dplyr::select(2,3,8:10,15,17,18) %>%
  filter(substr(Label,0,4) == sampleID) %>%
  filter(Area >= 0.005) %>%
  summarise(median = median(Area))


temp0 <- df_particles %>%
  dplyr::select(2,3,8:10,15,17,18) %>%
  filter(substr(Label,0,4) == sampleID) %>%
  filter(Area >= 0.005) %>%
  ggplot() +
  geom_histogram(bins = 30, aes(x = Area)) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  geom_vline(xintercept = as.numeric(mean1), color = "red",linetype = "dashed", size = 2) +
  #geom_vline(xintercept = as.numeric(median1), color = "blue",linetype = "dashed", size = 2) +
  theme_classic() +
  #ylab("cts") +
  theme(axis.text.x = element_text(colour = "black", size = 28,face = "bold"),
        axis.text.y = element_text(colour = "black", size = 28,face = "bold"),
        axis.ticks = element_line(colour = "black", size = 2),
        axis.line = element_line(colour = 'black', size = 2),
        axis.title.x = element_text(colour = "black", size = 28,face = "bold"),
        axis.title.y = element_text(colour = "black", size = 28,face = "bold"))

rm(mean1)
rm(median1)
rm(sampleID)

print(temp0)
ggsave(filename = "./extradata/plotexport0.png", plot = temp0, device = "png", width = 6, height = 6, units = "in")
rm(temp0)
```

```{r}
temp3 <- one %>%
  filter(hrs == 10) %>%
  filter(Ni.Vol.Corrected != 0.24) %>%
  filter(Ni.Vol.Corrected != 0.28) %>%
  filter(Ni.Vol.Corrected != 0.35) %>%
  ggplot() +
  geom_point(aes(x = Temp, y = R3,
                 size = 1,
                 color = as.factor(Ni.Vol.Corrected))) +
  xlab(expression(Temp~'['*degree*C*']')) +
  ylab(expression(R^3~'['*mu*m^3*']')) +
  theme_classic() +
  scale_y_log10(limits = c(0.002,25), sec.axis = sec_axis(~.^(1/3)*2, name = expression(D~'['*mu*m*']'))) +
  scale_x_continuous(limits = c(700,1100), sec.axis = sec_axis(~., labels = NULL)) +
  scale_color_manual(values=c("#CD9600", "#7CAE00", "#C77CFF")) +
  guides(colour = guide_legend(title = "Ni Vol.", override.aes = list(size=4), title.theme = element_text(colour="black", size = 12))) +
  annotation_logticks(sides = "l") +
  guides(size = FALSE) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12))


print(temp3)
ggsave(filename = "./extradata/plotexport3.png", plot = temp3, device = "png", width = 6,height = 4, units = "in")
rm(temp3)
```

```{r, results='hide'}
#10hr models

mod40 <- one %>%
  filter(Ni.Vol.Corrected == 0.40) %>%
  filter(Temp >= 800) %>%
  filter(hrs == 10) %>%
  lm(zz~z,.) %>%
  coef()
  #summary()

mod20 <- one %>%
  filter(Ni.Vol.Corrected == 0.20) %>%
  filter(Temp >= 800) %>%
  filter(hrs == 10) %>%
  lm(zz~z,.)%>%
  coef()
  #summary()

mod10 <- one %>%
  filter(Ni.Vol.Corrected == 0.10) %>%
  filter(Temp >= 800) %>%
  filter(hrs == 10) %>%
  lm(zz~z,.)%>%
  coef()
  #summary()
```

```{r, fig.cap="10hr linear models", fig.show='asis'}
#10 hour linear models, fitting without 700 datapoints
one %>%
  filter(hrs == 10) %>%
  filter(Ni.Vol.Corrected != 0.24) %>%
  filter(Ni.Vol.Corrected != 0.28) %>%
  filter(Ni.Vol.Corrected != 0.35) %>%
  ggplot() +
  geom_point(aes(x = z, y = zz, 
                 color = as.factor(Ni.Vol.Corrected))) +
  geom_abline(slope = as.numeric(mod40[2]),intercept = as.numeric(mod40[1])) +
  geom_abline(slope = as.numeric(mod20[2]),intercept = as.numeric(mod20[1])) +
  geom_abline(slope = as.numeric(mod10[2]),intercept = as.numeric(mod10[1])) +
  ylab(expression(ln(T*R^3/t))) +
  xlab("1/T") +
  theme_classic() +
  scale_color_manual(values=c("#CD9600", "#7CAE00", "#C77CFF"))
```



```{r, results='hide'}
#5hr models
#A linear model may be constructed for both five hour data series (24% and 35% Ni).

mod35 <- one %>%
  filter(Ni.Vol.Corrected == 0.35) %>%
  filter(hrs <= 5) %>%
  filter(Temp >= 800) %>%
  filter(Temp <= 1000) %>%
  lm(zz~z,.) %>%
  coef()
  #summary()

mod24 <- one %>%
  filter(Ni.Vol.Corrected == 0.24) %>%
  filter(hrs <= 5) %>%
  filter(Temp >= 800) %>%
  filter(Temp <= 1000) %>%
  lm(zz~z,.) %>%
  coef()
  #summary()
```

```{r, fig.cap="Particle size data for samples sintered for 5hrs. a) All nickel contents. b) 24% and 35% plotted for clarity of increasing particle size trend due to increased nickel content."}

one %>%
  filter(hrs <= 5) %>%
  ggplot() +
  geom_point(aes(x = z, y = zz, 
                 color = as.factor(Ni.Vol.Corrected))) +
  ylab(expression(ln(T*R^3/t))) +
  xlab("1/T") +
  theme_classic()

one %>%
  filter(Ni.Vol.Corrected <= 0.35) %>%
  filter(Ni.Vol.Corrected >= 0.24) %>%
  filter(Ni.Vol.Corrected != 0.28) %>%
  filter(hrs <= 5) %>%
  ggplot() +
  geom_point(aes(x = z, y = zz, 
                 color = as.factor(Ni.Vol.Corrected))) +
  ylab(expression(ln(T*R^3/t))) +
  xlab("1/T") +
  theme_classic() +
  scale_color_manual(values=c("#00BE67", "#00A9FF")) +
  geom_abline(slope = as.numeric(mod35[2]),intercept = as.numeric(mod35[1])) +
  geom_abline(slope = as.numeric(mod24[2]),intercept = as.numeric(mod24[1]))

#5hr linear models

#mod10[2]*-8.617E-5
#mod20[2]*-8.617E-5
#mod40[2]*-8.617E-5
#mod24[2]*-8.617E-5
#mod35[2]*-8.617E-5

```

```{r}
#regsubsets model: LSW + (composition variable included) plotting

temp5 <- one %>%
  filter(Temp >= 800) %>%
  ggplot() +
  geom_point(size = 2,aes(x = z*1000, y = zz, 
                 shape = as.factor(hrs),
                 
                 color = Ni.Vol.Corrected)) +
  ylab(expression(ln~(T*R^'3'*'/'~t))) +
  xlab(expression('1000'*'/'*T~~'['*degree*C*']'^-'1')) +
  theme_classic() +
  scale_y_continuous(limits = c(-2,10), 
                     sec.axis = sec_axis(~., labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  scale_shape_manual(values=c(16, 17, 0, 2)) +
  scale_color_gradientn(colours = hue_pal()(8)) +
  guides(shape = guide_legend(title = "Time [hrs]", 
                              title.theme = element_text(colour="black", 
                                                         size = 12)),
         size = FALSE,
         color = guide_colorbar(title = "Ni Vol.", title.theme = element_text(colour="black", size = 12))) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12)) +
  geom_abline(slope = as.numeric(coef(regmod,2)[2])/1000, 
              intercept = as.numeric(coef(regmod,2)[1]) + as.numeric(coef(regmod,2)[3])*0.5) +
  geom_abline(slope = as.numeric(coef(regmod,2)[2])/1000, 
              intercept = as.numeric(coef(regmod,2)[1])) +
  annotate("text", x = 0.76, y = 0, fontface = 1,
           label = paste("Ea =", round(coef(regmod,2)[2]*-8.617E-5,3),"eV")) +
  annotate("text", x = 0.76, y = 1, fontface = 1,
           label = paste("Adj. Rsq =", round(cms$adj.r.squared,2)))

print(temp5)

ggsave(filename = "./extradata/plotexport5.png", plot = temp5, 
       device = "png", width = 6,height = 4, units = "in")

rm(temp5)
```

```{r, fig.cap="Histograms"}
#histrograms are worse than density functions in terms of clarity

two %>%
  arrange(Temp) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  group_by(Label) %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_histogram(bins = 30, aes(x = Area, color = as.factor(Temp))) +
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  #guides(color = FALSE) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL))

two %>%
  arrange(Temp) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_histogram(bins = 30, aes(x = Area, group = Label, color = as.factor(Temp))) +
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  #guides(color = FALSE) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL))

two %>%
  arrange(Temp) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_histogram(bins = 30, aes(x = Area, group = Label, color = Label)) +
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  #guides(color = FALSE) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL))
```

```{r}
#density plot exploration
df_particles %>%
  #mutate(Label = substr(Label,0,4)) %>%
  filter(Label != "WH15B") %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = Label)) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  guides(color = FALSE)

df_particles %>%
  #mutate(Label = substr(Label,0,4)) %>%
  filter(Label != "WH15B") %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = R3, y = ..density.., group = Label, 
                   color = as.factor(Temp))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic()

df_particles %>%
  mutate(Label = substr(Label,0,4)) %>%
  filter(Label != "WH15B") %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = R3, y = ..density.., group = Label, 
                   color = as.factor(Temp))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic()
```

```{r}
df_particles %>%
  mutate(Label = substr(Label,0,4)) %>%
  filter(Label != "WH15B") %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = R3, y = ..density.., group = Label,
                   fill = Temp, color = Temp), alpha = 0.01) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  #scale_y_log10(sec.axis = sec_axis(~., labels = NULL))
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  scale_fill_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  scale_color_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  guides(color = FALSE)

df_particles %>%
  mutate(Label = substr(Label,0,4)) %>%
  filter(Label != "WH15B") %>%
  filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(R3, group = Label,
                   stat(count),
                   fill = Temp, color = Temp), alpha = 0.01) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  #scale_y_log10(sec.axis = sec_axis(~., labels = NULL))
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  scale_fill_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  scale_color_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  guides(color = FALSE)

  #scale_fill_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  #scale_color_gradientn(colours = wes_palette(n = 5,name = "Zissou1")) +
  #guides(color = FALSE)
```

```{r}
two %>%
  filter(Temp == 700) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle("700C")

two %>%
  filter(Temp == 800) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle("800C")

two %>%
  filter(Temp == 900) %>%
  filter(Label != "WH15B") %>%
  #mutate(Label = substr(Label,0,4)) %>%
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle("900C")

two %>%
  filter(Temp == 1000) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle("1000C")

two %>%
  filter(Temp == 1100) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(aes(x = Area, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle("1100C")
```

```{r}
#Label List
df_particles %>%
  dplyr::select(Label) %>%
  #mutate(Label = substr(Label,0,4)) %>%
  unique()

sampleID <- "WH09"

#weibull parameter estimation
df_particles %>%
  filter(substr(Label,0,4) == sampleID) %>%
  #filter(Area >= 0.005) %>%
  dplyr::select(Area) %>%
  unlist() %>%
  unname() %>%
  fitdistr(.,densfun = "weibull")

#log normal parameter estimation
df_particles %>%
  filter(substr(Label,0,4) == sampleID) %>%
  #filter(Area >= 0.005) %>%
  dplyr::select(Area) %>%
  unlist() %>%
  unname() %>%
  fitdistr(.,densfun = "log-normal")

#need to merge with density dataframe to attribute the sample info to each label
#color by temperature and time or composition rather than
#Label, which is meaningless
#convert to R3?
#need to take log of area to fit a log based distribution?

#dweibull()
#dlnorm()

rm(sampleID)
```

```{r}
#comparison between R3 and Area, finding the correct data flow

sampleID <- "WH02A"

r3line <- one %>%
  filter(Label == sampleID) %>%
  dplyr::select(R3)
as.numeric(r3line)

tempMeanArea <- two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%
  dplyr::pull(Area) %>%
  mean()

two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%
  dplyr::pull(Area) %>%
  mean() %>%
  sqrt() %>% '^'(3)
  
tempr3m <- two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%  
  dplyr::pull(R3) %>%
  mean()

two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%
  ggplot() +
  geom_density(aes(x = R3, y = ..density.., group = Label, color = as.factor(hrs))) + 
  geom_density(aes(x = Area, y = ..density.., group = Label, color = "blue")) +
  #geom_histogram(aes(x = R3, y = ..density.., group = Label, color = as.factor(hrs))) +
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle(sampleID) +
  geom_vline(xintercept = as.numeric(r3line), color = "red") +
  geom_vline(xintercept = as.numeric(tempr3m), color = "blue") +
  geom_vline(xintercept = as.numeric(tempMeanArea), color = "black")

two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%
  pull(R3) %>%
  density()

two %>%
  filter(Label == sampleID) %>%
  filter(Area >= 0.005) %>%
  dplyr::select(R3) %>%
  summary()
```

```{r}
#peak fitting attempt
sampleID <- "WH04B"

r3line <- one %>%
  filter(Label == sampleID) %>%
  dplyr::select(R3)

BIC <- two %>%
  filter(Label == sampleID) %>%
  dplyr::select(R3) %>%
  mclustBIC(verbose = FALSE)

Model <- two %>%
  filter(Label == sampleID) %>%
  dplyr::select(R3) %>%
  mclustModel(., BIC)

Model$parameters$mean

two %>%
  filter(Label == sampleID) %>%
  ggplot() +
  geom_density(aes(x = R3, y = ..density.., group = Label, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  #guides(color = FALSE) +
  ggtitle(sampleID) +
  geom_vline(xintercept = Model$parameters$mean) +
  geom_vline(xintercept = as.numeric(r3line), color = "red")

rm(sampleID)
rm(BIC)
rm(Model)
rm(r3line)
```


<!--
```{r}
#second peak fitting for high temperature 5 hours and long time 900
#this is a looped output of the above code chunk

idlist1 <- two %>%
  filter(Temp >= 1000) %>%
  #filter(Label != "WH06C") %>% #Bad fit
  dplyr::select(Label) %>%
  unique()

idlist2 <- two %>%
  filter(hrs >= 50) %>%
  dplyr::select(Label) %>%
  unique()

idlist <- rbind(idlist1,idlist2)

pk2df <- data.frame()

for (i in idlist[,1]){
  
  temp1 <- two %>%
    filter(Label == i) %>%
    dplyr::select(R3) %>%
    mclustBIC(verbose = FALSE)

  temp2 <- two %>%
    filter(Label == i) %>%
    dplyr::select(R3) %>%
    mclustModel(., temp1)
  
  temp3 <- temp2$parameters$mean
  
  r3line <- one %>%
    filter(Label == i) %>%
    dplyr::select(R3)
  
  tempdata <- data.frame(i, as.numeric(r3line), temp3)
  
  pk2df <- rbind(pk2df, tempdata)
  rm(tempdata)
  #outputs a df containing the mean R3 and means from mclustModel
  
  #plotting of mclustModel means over density function, with total mean R3 in red
  plot1 <- two %>%
    filter(Label == i) %>%
    ggplot() +
    geom_density(aes(x = R3, y = ..density.., group = Label, color = as.factor(hrs))) +
    scale_x_log10(sec.axis = sec_axis(~., labels = NULL)) +
    scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
    theme_classic() +
    #guides(color = FALSE) +
    ggtitle(i) +
    geom_vline(xintercept = temp2$parameters$mean) +
    geom_vline(xintercept = as.numeric(r3line), color = "red")
  
  print(plot1)
  
  
}

colnames(pk2df) <- c("Label","meanr3","pk2")

rm(r3line)
rm(plot1)
rm(temp1)
rm(temp2)
rm(temp3)
rm(i)
rm(idlist1)
rm(idlist2)
rm(idlist)
```
-->


<!--

## Concentration mapping

```{r}
#ni_map <- read.csv("./extradata/Ni-map.csv")

ni_line <- read.csv("./extradata/Ni-line.csv")

colnames(ni_line)[1] <- "distx"

colnames(ni_line)[2] <- "cts"

ni_line <- ni_line[,1:2]


```

```{r}
ni_line %>%
  ggplot(aes(x = distx, y = cts)) +
  geom_point() +
  theme_classic()
```
-->

<!--
## LTO-Ni DIL

```{r}
read.table("../NASA/Characterization/DIL/LTO-Dil/LTONi1.ASC", skip = 27) %>%
  ggplot() +
  geom_point(aes(x=V2,y=V3))

read.table("../NASA/Characterization/DIL/LTO-Dil/LTO-02.ASC", skip = 27) %>%
  ggplot() +
  geom_point(aes(x=V2,y=V3))
```
-->

<!--
```{r}
#find means for a given label and replace to missing values
fractSum %>%
  filter(substr(Label,1,4) == "WH12") %>%
  filter(is.na(R3) == FALSE) %>%
  pull(R3) %>%
  mean()

fractSum %>%
  filter(substr(Label,1,4) == "WH12") %>%
  filter(is.na(Th.Density) == FALSE) %>%
  pull(Th.Density) %>%
  mean()


#example of replacing the data
fractSum <- fractSum %>%
  mutate(R3 = if_else(substr(Label,1,4) == "WH12",
                      replace(R3,is.na(R3),1.051741),
                      R3))

fractSum <- fractSum %>%
  mutate(Th.Density = if_else(substr(Label,1,4) == "WH12",
                      replace(Th.Density,is.na(Th.Density),92.42108),
                      Th.Density))

fractSum <- fractSum %>%
  mutate(Ni.Vol.Corrected = if_else(substr(Label,1,4) == "WH12",
                                    replace(Ni.Vol.Corrected,is.na(Ni.Vol.Corrected),0.24),
                                    Ni.Vol.Corrected))
```

```{r}
fractSum %>%
  filter(substr(Label,1,4) == "WH15") %>%
  filter(is.na(R3) == FALSE) %>%
  pull(R3) %>%
  mean()

fractSum %>%
  filter(substr(Label,1,4) == "WH15") %>%
  filter(is.na(Th.Density) == FALSE) %>%
  pull(Th.Density) %>%
  mean()

fractSum <- fractSum %>%
  mutate(R3 = if_else(substr(Label,1,4) == "WH15",
                      replace(R3,is.na(R3),6.240454),
                      R3))

fractSum <- fractSum %>%
  mutate(Ni.Vol.Corrected = if_else(substr(Label,1,4) == "WH15",
                                    replace(Ni.Vol.Corrected,is.na(Ni.Vol.Corrected),0.50),
                                    Ni.Vol.Corrected))

fractSum <- fractSum %>%
  mutate(Th.Density = if_else(substr(Label,1,4) == "WH15",
                      replace(Th.Density,is.na(Th.Density),93.90703),
                      Th.Density))
```

```{r}
fractSum <- fractSum %>%
  mutate(Ni.Vol.Corrected = if_else(substr(Label,1,4) == "WH07",
                                    replace(Ni.Vol.Corrected,is.na(Ni.Vol.Corrected),0.0),
                                    Ni.Vol.Corrected))

fractSum <- fractSum %>%
  mutate(Ni.Vol.Corrected = if_else(substr(Label,1,4) == "WH20",
                                    replace(Ni.Vol.Corrected,is.na(Ni.Vol.Corrected),0.35),
                                    Ni.Vol.Corrected))

fractSum <- fractSum %>%
  mutate(Th.Density = if_else(Label == "WH07A",
                      replace(Th.Density,is.na(Th.Density),90.49685),
                      Th.Density))

fractSum <- fractSum %>%
  mutate(Th.Density = if_else(Label == "WH07B",
                      replace(Th.Density,is.na(Th.Density),89.02054),
                      Th.Density))

fractSum <- fractSum %>%
  mutate(Th.Density = if_else(Label == "WH20A",
                      replace(Th.Density,is.na(Th.Density),55.16284),
                      Th.Density))


#filler program
#create a dataframe with all the average values
#using the summarise function
#define a function for mutation such that
#mutate(desiredvalue = function(Temp,time,Ni))

#example
fractSum %>%
  mutate(LabelAve = substr(Label,1,4)) %>%
  group_by(LabelAve) %>%
  summarise(aveDen = mean(Th.Density))

```
-->



<!--
```{r}
#temp R3 density

tempz <- df_particles %>%
  filter(Label != "WH19A") %>%
  mutate(Label = substr(Label,0,4)) %>%
  #
  group_by(Label) %>%
  mutate(rstar = R3/mean(R3)) %>%
  #
  filter(Label != "WH15B") %>%
  filter(Area >= 0.005) %>%
  filter(hrs == 5) %>%
  filter(Label != "WH19") %>%
  filter(Ni.Vol.Corrected == 0.35) %>%
  ggplot() +
  geom_density(size = 1, aes(x = R3, y = ..density.., group = Temp, 
                   color = as.factor(Temp))) + 
  scale_x_log10(sec.axis = sec_axis(~.^(1/3)*2, name = expression(D~'['*mu*m*']')),
                limits = c(0.0001, 100000),
                breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_continuous(limits = c(0,0.53), expand = c(0, 0), sec.axis = sec_axis(~., labels = NULL)) +
  geom_hline(yintercept = 0, color = "White", size = 1.5) +
  theme_classic() +
  ylab("Normalized PSD") +
  xlab(expression(R^3~'['*mu*m^3*']')) +
  #annotation_logticks(sides = "b") +
  guides(colour = guide_legend(title = expression(bold(Temp~'['*degree*C*']'), 
                               #override.aes = list(size=4), 
                               title.theme = element_text(colour = "black",
                                                          face = "bold",
                                                          size = 12)))) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12))
print(tempz)
ggsave(filename = "./extradata/plotexportz.png", plot = tempz, 
       device = "png", width = 6,height = 4, units = "in")
rm(tempz)
```

```{r}
#nickel R3 density

tempx <- df_particles %>%
  mutate(Label = substr(Label,0,4)) %>%
  #
  group_by(Label) %>%
  mutate(rstar = R3/mean(R3)) %>%
  #
  filter(Label != "WH15B") %>%
  filter(Area >= 0.005) %>%
  filter(Label != "WH19") %>%
  filter(Temp == 900) %>%
  filter(hrs == 5) %>%
  ggplot() +
  geom_density(size = 1, aes(x = R3, y = ..density.., group = Ni.Vol.Corrected, 
                   color = as.factor(Ni.Vol.Corrected))) + 
  scale_x_log10(sec.axis = sec_axis(~.^(1/3)*2, name = expression(D~'['*mu*m*']')),
                limits = c(0.0001, 100000),
                breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_continuous(limits = c(0,0.53), expand = c(0, 0), sec.axis = sec_axis(~., labels = NULL)) +
  geom_hline(yintercept = 0, color = "White", size = 1.5) +
  theme_classic() +
  ylab("Normalized PSD") +
  xlab(expression(R^3~'['*mu*m^3*']')) +
  #annotation_logticks(sides = "tb") +
  guides(colour = guide_legend(title = "Ni Vol.", 
                               #override.aes = list(size=4), 
                               title.theme = element_text(colour = "black",
                                                          face = "bold",
                                                          size = 12))) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12))
print(tempx)
ggsave(filename = "./extradata/plotexportx.png", plot = tempx, 
       device = "png", width = 6, height = 4, units = "in")
rm(tempx)
```

```{r}
#time R3 density

tempzz <- df_particles %>%
  filter(Temp == 900) %>% #Temperature of interest
  filter(Area >= 0.005) %>% #Noise reduction
  filter(Label != "WH15B") %>% #weird distro
  filter(Ni.Vol.Corrected == 0.35) %>%
  mutate(Label = substr(Label,0,4)) %>%
  #filter(Ni.Vol.Corrected == 0.28) %>%
  #filter(Label != "WH31") %>%
  #filter(Label != "WH37") %>%
  #
  group_by(Label) %>%
  mutate(rstar = R3/mean(R3)) %>%
  #
  #filter(Area >= 0.002) %>%
  ggplot() +
  geom_density(size = 1, aes(x = R3, y = ..density.., group = hrs, color = as.factor(hrs))) + 
  scale_x_log10(sec.axis = sec_axis(~.^(1/3)*2, name = expression(D~'['*mu*m*']')),
                limits = c(0.0001, 100000),
                breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  scale_y_continuous(limits = c(0,0.53), expand = c(0, 0), sec.axis = sec_axis(~., labels = NULL)) +
  theme_classic() +
  guides(colour = guide_legend(title = "Time [hrs]", 
                               #override.aes = list(size=4), 
                               title.theme = element_text(colour="black",
                                                          face = "bold",
                                                          size = 12))) +
  ylab("Normalized PSD") +
  xlab(expression(R^3~'['*mu*m^3*']')) +
  geom_hline(yintercept = 0, color = "White", size = 1.5) +
  #annotation_logticks() +
  scale_color_manual(values=c("#00BF7D", "#BF7D00", "#7C00BF", "#BF0041")) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12))

print(tempzz)
ggsave(filename = "./extradata/plotexportzz.png", plot = tempzz, 
       device = "png", width = 6,height = 4, units = "in")
rm(tempzz)
```
-->


## Peak Fitting

```{r}
#peakfits from KGP python code

peakfits <- read.csv("./extradata/SG1-G2_density-fit-params_fine.csv")

peakfits$filename <- as.character(peakfits$filename)

peakfits <- peakfits %>%
  mutate(Labelfine = substr(filename,1,nchar(filename) - 5)) %>%
  mutate(Label = substr(Labelfine,1,5))


temppeakfits <- merge(peakfits, one, by = "Label", all = TRUE) %>%
  filter(Label != "WH15B") %>%
  #mutate(pkfity = if_else(WHpeakNum == 2, 10^(G2_center), 10^(SG1_center))) %>%
  #filter(is.na(Temp)) %>%
  ggplot() +
  geom_point(aes(x = Temp, y = 10^(SG1_center),
                 size = 1,
                 color = as.factor(Ni.Vol.Corrected))) +
  geom_point(aes(x = Temp, y = 10^(G2_center),
                 size = 1,
                 color = as.factor(Ni.Vol.Corrected))) +
  #
  #
  xlab(expression(Temp~'['*degree*C*']')) +
  ylab(expression(R^3~'['*mu*m^3*']')) +
  theme_classic() +
  scale_y_log10(limits = c(0.002,25), sec.axis = sec_axis(~.^(1/3)*2, name = expression(D~'['*mu*m*']'))) +
  scale_x_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  guides(colour = guide_legend(title = "Ni Vol.", 
                               override.aes = list(size=4), 
                               title.theme = element_text(colour="black", size = 12))) +
  annotation_logticks(sides = "l") +
  guides(size = FALSE) +
  theme(axis.text.x = element_text(colour = "black", size = 16),
        axis.text.y = element_text(colour = "black", size = 16),
        axis.ticks = element_line(colour = "black", size = 1),
        axis.line = element_line(colour = 'black', size = 1),
        axis.title.x = element_text(colour = "black", size = 16),
        axis.title.y = element_text(colour = "black", size = 16),
        legend.text = element_text(colour="black", size = 12))

print(temppeakfits)
ggsave(filename = "./extradata/plotexportpeakfits.png", plot = temppeakfits, 
       device = "png", width = 6,height = 4, units = "in")
rm(temppeakfits)

```


```{r}
read.table(file = "./extradata/Dlc-Pixel-Sum-900-5-35B0006.txt",
           header = TRUE) %>%
  ggplot() +
  geom_point(size = 0.1, aes(x = X, y = -Y,
                 color = Local.Fractal.Dimension)) +
  scale_y_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~., labels = NULL)) +
  scale_color_gradientn(colours = hue_pal()(8)) +
  theme_classic() +
  coord_fixed()
```



<!--
```{r}
#for hardness, check real nickel values

nine %>%
  select(Temp, hrs, Label, Labelfine, totNifrac, Ni.Vol.Corrected) %>%
  unique() %>%
  filter(Temp >= 800) %>%
  filter(hrs == 5) %>%
  ggplot() +
  geom_point(aes(x = Ni.Vol.Corrected, y = totNifrac,
                 color = as.factor(hrs))) +
  geom_abline(slope = 1, intercept = 0)


nine %>%
  select(Temp, hrs, Label, Labelfine, totNifrac, Ni.Vol.Corrected) %>%
  unique() %>%
  filter(Temp >= 800) %>%
  filter(hrs == 5) %>%
  filter(Ni.Vol.Corrected == 0.28) %>%
  arrange(desc(totNifrac))
```

<!--
## Color Palette Help

```{r, echo=FALSE, fig.show='hide', fig.cap="ggplot2 colors help"}
#ggplot2 colors help

show_col(hue_pal()(8))

#show_col(hue_pal()(8))

hue_pal()(8)
```
