---
title: "LTO-Ni-Pairs"
output: html_document
date: "2023-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

save <- 1
```

```{r}
bind1 <- voronoidens %>%
  select(-x, -count, -density, -Labelfineshort) %>%
  select(-magx, -imagearea, -avennd) %>%
  select(-avecountarea,-avevcoarse, -countperarea) %>%
  #select(-Ni.Vol.Corrected) %>%
  select(-stressf, -aveR3) %>%
  #
  filter(Label != "WH13A") %>% #weird outlier
  filter(Label != "WH15B") %>%
  filter(Labelfine != "WH06A/1000-5-35A0006.tiff") %>%
  filter(Labelfine != "WH06C/1000-5-35C0004.tiff") %>%
  #select(-Label, -Labelfine) %>%
  #
  unique()

#bind2 allows the PCA dataset to be filtered down to Magx = 10 (machine learning doesn't have Magx=5)
bind2 <- df_particles_fine %>%
  select(Labelfine, magx) %>%
  unique()

#bind 3 brings in skeleton data
bind3 <- skeleton.data %>%
  select(ave.branches, ave.ave.branches, ave.max.branches, Labelfine) %>%
  unique()

temppairs <- left_join(bind1,bind3, by = "Labelfine")


#add PC results to bind1 then bind3
# temp <- left_join(prcomp.R3.Results, bind2, by = "Labelfine") %>%
#   filter(magx == 10) %>%
#   select(1:7) %>%
#   left_join(., bind1, by = "Labelfine") %>%
#   left_join(., bind3, by = "Labelfine") %>%
#   select(-Label, -Labelfine) %>%
#   mutate(condAve = log(condAve)) %>%
#   filter(is.na(condAve) == FALSE)
```

```{r}
pairsplottemp <- temppairs %>%
  mutate(condAve = log10(condAve)) %>%
  select(-Label,-Labelfine) %>%
  select(Ni.Vol.Corrected, Temp, hrs,Th.Density,
         totNifrace,finecount,aveAreafine,
         fineavennd,
         voronoicount,avevoronoix,
         ave.branches,ave.ave.branches,ave.max.branches,
         condAve
         ) %>%
  rename(.,"Nominal Nickel Fraction"="Ni.Vol.Corrected") %>%
  rename(.,"Average Branch Length"="ave.ave.branches") %>%
  rename(.,"Maximum Branch Length"="ave.max.branches") %>%
  rename(.,"Average Number of Branches"="ave.branches") %>%
  rename(.,"Average Particle Area"="aveAreafine") %>%
  rename(.,"Average Edge-to-Edge Spacing"="avevoronoix") %>%
  rename(.,"Average Center-to-Center Spacing"="fineavennd") %>%
  rename(.,"Counts Per Area"="finecount") %>%
  rename(.,"Dwell Time"="hrs") %>%
  rename(.,"Sintering Temperature"="Temp") %>%
  rename(.,"Bulk Density"="Th.Density") %>%
  rename(.,"Nickel Area Fraction"="totNifrace") %>%
  rename(.,"Edge-to-Edge Complexity"="voronoicount") %>%
  rename(., "Conductivity"="condAve") %>%
  
  ggpairs(labeller = label_wrap_gen(10))

#names(temppairs)
  
```

```{r}
pairsplottemp
```


```{r}
{if(save == 1)ggsave(filename = "./paperexports/plotexportpairs.png", plot = pairsplottemp, 
       device = "png", width = 10,height = 10, units = "in")} #ggsave has a dpi setting
```



<!--
```{r}
#pair correlation plots


fcpairs <- df_particles_fine %>%
  filter(condAve >= 0.01) %>%
  #mutate(R3 = log(R3)) %>%
  mutate(condAve = log10(condAve)) %>%
  filter(aveR3 <= 45) %>%
  select(-Label, -Temp, -z) %>%
  select(Ni.Vol.Corrected, Tempk, hrs, Th.Density, aveR3, 
         zz, zzz,
         avennd, avecountarea,
         condAve, stressf) %>%
  unique() %>%
  ggpairs(aes(color = as.factor(Ni.Vol.Corrected)))

print(fcpairs)

{if(save == 1)ggsave(filename = "./nndexports/plotexportpairs.png", plot = fcpairs, 
       device = "png", width = 10,height = 8, units = "in")} #ggsave has a dpi setting
rm(fcpairs)
```
